R for Clinical Study Reports and Submission

### 2022-03-23 index.Rmd
Add events table

```{r, include=FALSE}
source("common.R")
```

@@

>>>>

@@

## Events {-}

```{css, echo=FALSE}
table.table td:nth-child(1) { min-width: 27ch; }
table.table td:nth-child(2) { min-width: 12ch; }
table.table td:nth-child(3) { min-width: 10ch; }
table.table tbody { border-bottom: 1px solid #B6BDC6; }
```

```{r, echo=FALSE}
knitr::kable(read.table("events.tsv", stringsAsFactors = FALSE, header = TRUE, sep = "\t"))
```
